Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-29 snapshot_system/fast14_evaluation.tex
figure updates, make now builds fast14_main

\begin{figure}[ht]
    \centering
    \begin{subfigure}%{.5\textwidth}
      \centering
      %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
            \begin{tikzpicture}
                    \begin{axis}[
                    tick label style={font=\scriptsize},
                    tick style=thin,
                    width=0.5\linewidth,
                    title={\small $p=100$},
                    cycle list={
                        {blue,thin,solid,mark=none},
                        {red,thin,densely dashed,mark=none},
                        {red,thin,densely dotted,mark=none}
                    },
                    xlabel={\tiny Failed nodes},
                    ylabel={\tiny VM Availability (\%)},
                    extra y ticks={99.9}, %if important numbers are missing
                    mark options=solid,
                    legend columns=-1,
                    legend style={
                        font=\small\sffamily,
                        cells={anchor=west}, %legend entry alignment
                        legend pos=south west %legend position
                    },
                    legend to name=legend:vm-availability,
                    %reverse legend,
                    ]
                    \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                    \addlegendentry{VO\,$6.3$ (optimistic)}
                    \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                    \addlegendentry{VC (expected)}
                    \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                    \addlegendentry{VC (worst-case)}
                    %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                    %\addlegendentry{VO\,$20$ (optimistic)}
                    \end{axis}
            \end{tikzpicture}
      %\caption{100 machine cluster.}
      \label{fig:vm-availability-100}
    \end{subfigure}%
    \begin{subfigure}%{.5\textwidth}
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
            \pgfplotsset{/pgf/number format/.cd,
                fixed,precision=4}
		\begin{axis}[
                    width=0.5\linewidth,
                    tick label style={font=\scriptsize},
                    tick style=thin,
		title={\small $p=1000$},
                cycle list={
                    {blue,thin,solid,mark=none},
                    {red,thin,densely dashed,mark=none},
                    {red,thin,densely dotted,mark=none}
                },
		xlabel={\tiny Failed nodes},
		ylabel={\tiny VM Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
                %\addlegendentry{$VO\,6.3$ (optimistic)}
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
                %\addlegendentry{$VC\,1250$ (estimated)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
                %\addlegendentry{$VC\,2500000$ (worst-case)}
                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                %\addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
        %\caption{100000 machine cluster.}
  \label{fig:vm-availability-100000}
\end{subfigure}
    \pgfplotslegendfromname{legend:vm-availability}
      \caption{Availability of VM backup snapshots for VO and VC when failed machines vary
from 1 to 10.  Non-PDS replication is fixed
          at 3 and PDS replication is 4. 
      }
      \label{fig:vm-availability}

>>>>

\begin{figure}[ht]
    \centering
    \begin{subfigure}%{.5\textwidth}
      \centering
      %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
            \begin{tikzpicture}
                    \begin{axis}[
                    tick label style={font=\scriptsize},
                    tick style=thin,
                    width=0.5\linewidth,
                    title={\small $p=100$},
                    cycle list={
                        {blue,thin,solid,mark=none},
                        {red,thin,densely dashed,mark=none},
                        {red,thin,densely dotted,mark=none}
                    },
                    xlabel={\tiny Failed nodes},
                    ylabel={\tiny VM Availability (\%)},
                    extra y ticks={99.9}, %if important numbers are missing
                    mark options=solid,
                    legend columns=-1,
                    legend style={
                        font=\small\sffamily,
                        cells={anchor=west}, %legend entry alignment
                        legend pos=south west %legend position
                    },
                    legend to name=legend:vm-availability,
                    %reverse legend,
                    ]
                    \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                    \addlegendentry{VO}
                    \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                    \addlegendentry{VC}
                    \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                    \addlegendentry{VC (worst-case)}
                    %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                    %\addlegendentry{VO\,$20$ (optimistic)}
                    \end{axis}
            \end{tikzpicture}
      %\caption{100 machine cluster.}
      \label{fig:vm-availability-100}
    \end{subfigure}%
    \begin{subfigure}%{.5\textwidth}
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
            \pgfplotsset{/pgf/number format/.cd,
                fixed,precision=4}
		\begin{axis}[
                    width=0.5\linewidth,
                    tick label style={font=\scriptsize},
                    tick style=thin,
		title={\small $p=1000$},
                ymin=099.9991,
                ymax=100.0002,
                %ytick=data,
                %yticklabels from table={figures/vm_availability_1000.txt}{[index]1},
                cycle list={
                    {blue,thin,solid,mark=none},
                    {red,thin,densely dashed,mark=none},
                    {red,thin,densely dotted,mark=none}
                },
		xlabel={\tiny Failed nodes},
		ylabel={\tiny VM Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
                %\addplot table[x=NodesFailed,y expr=(\thisrow{VO1}-99.999)*1000]{figures/vm_availability_1000.txt};
                %\addlegendentry{$VO\,6.3$ (optimistic)}
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC1}-99.999)*1000]{figures/vm_availability_1000.txt};
                %\addlegendentry{$VC\,1250$ (estimated)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC2}-99.999)*1000]{figures/vm_availability_1000.txt};
                %\addlegendentry{$VC\,2500000$ (worst-case)}
                %\addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                %\addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
        %\caption{100000 machine cluster.}
  \label{fig:vm-availability-100000}
\end{subfigure}
    \pgfplotslegendfromname{legend:vm-availability}
      \caption{Availability of VM backup snapshots for VO and VC when failed machines vary
from 1 to 10.  Non-PDS replication is fixed
          at 3 and PDS replication is 4. 
      }
      \label{fig:vm-availability}
